The K2 Halo Photometry Campaign

### 2019-03-20 paper/ms.tex
autograd citation
introduction

% intro kepler

% briefly intro the halo method and halo literature

% describe contents of paper: code, catalog, categorization, conclusions

@@

\noindent which can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length.

% smear
This method differs from smear photometry \citep{Pope2016}, which uses collateral `smear' data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD. While this has also been used for photometry of very bright stars, the `halo' method has the advantage of averaging over many more realizations of the K2 pointing systematics and permitting more significant calibration, achieving a generally higher photometric prevision.

>>>>

% intro kepler
The \kepler Space Telescope was launched with a goal of determining the frequency of Earth-sized planets around Solar-like stars \citep{2010sci...327..977b}, a goal which it has substantially achieved \citep[e.g.][]{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}. In order to explore these populations it was necessary to observe hundreds of thousands of stars, with the consequence that the \kepler the exposure time and gain were set to optimally observe eleventh or twelfth-magnitude stars, while bright stars are saturated and these saturated stars were intentionally avoided. In the two-wheeled revival as the \ktwo mission, the \kepler telescope observed a sequence of ecliptic-plane fields containing many more very-saturated stars. While it is difficult to obtain precise light curves of these stars because of their saturation, they are some of the most-valuable targets to follow up with photon-hungry methods such as interferometry or high-resolution spectroscopy, and they typically have long histories of previous observations.

% briefly intro the halo method and halo literature
In order to recover precise photometry of the brightest stars in \ktwo, we have developed two main approaches, `smear' and `halo' photometry. Smear photometry \citep{Pope2016} uses collateral calibration data to recover light curves of stars which were not necessarily conventionally targeted. The more precise method of halo photometry, which is the subject of this paper, uses the broad `halo' of scattered light around a saturated star to recover relative photometry, by constructing a light curve as a linear combination of individual pixel time series and minimizing a Total Variation objective function (TV-min). It has been employed for example on the Pleiades \citep{White2017} and the brightest-ever star on \kepler silicon, Aldebaran \citep{Farr2018}, recovering photometry with a precision nearly that of normally-obtained \ktwo observations of unsaturated stars. Unlike smear, this requires downloading data out to a 12--20~pixel radius around each star, and has accordingly only been possible for stars that were specifically targeted with apertures optimized for this method and for a small number of other stars for which this is fortuitously the case.

% describe contents of paper: code, catalog, categorization, conclusions
In this Paper we describe the complete catalog of long-cadence \ktwo halo light curves which we have made publicly available. We have employed halo photometry on all stars targeted with appropriate apertures, and have done a preliminary characterization of interesting astrophysical variability. We also document the main changes in the halo data reduction pipeline, \texttt{halophot}, with respect to previous releases. These include oscillating red giants, pulsating and quiet main sequence stars, and eclipsing binaries, many of which are among the brightest objects of their type to have been observed with space photometry. We hope that this diverse catalog of light curves will be useful for an equally-diverse range of astrophysical investigations.

@@

\noindent which can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length. TV is a convex objective function and has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd};][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
% smear
This method differs from smear photometry \citep{Pope2016}, which uses collateral `smear' data to obtain a 1-D spatial profile with $\sim 1/1000$ of the flux on each CCD. While this has also been used for photometry of very bright stars, the `halo' method has the advantage of averaging over many more realizations of the K2 pointing systematics and permitting more significant calibration, achieving a generally higher photometric prevision.
